---
output:
  md_document:
    variant: markdown_github
html_preview: false
---

# ReactomePA: Reactome Pathway Analysis

[![platform](http://www.bioconductor.org/shields/availability/devel/ReactomePA.svg)](https://www.bioconductor.org/packages/devel/bioc/html/ReactomePA.html#archives)
[![Build Status](http://www.bioconductor.org/shields/build/devel/bioc/ReactomePA.svg)](https://bioconductor.org/checkResults/devel/bioc-LATEST/ReactomePA/)
[![Linux/Mac Travis Build Status](https://img.shields.io/travis/GuangchuangYu/ReactomePA/master.svg?label=Mac%20OSX%20%26%20Linux)](https://travis-ci.org/GuangchuangYu/ReactomePA)
[![AppVeyor Build Status](https://img.shields.io/appveyor/ci/Guangchuangyu/ReactomePA/master.svg?label=Windows)](https://ci.appveyor.com/project/GuangchuangYu/ReactomePA)
[![install with bioconda](https://img.shields.io/badge/install%20with-bioconda-green.svg?style=flat)](http://bioconda.github.io/recipes/bioconductor-reactomepa/README.html)

[![Project Status: Active - The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active)
[![codecov](https://codecov.io/gh/GuangchuangYu/ReactomePA/branch/master/graph/badge.svg)](https://codecov.io/gh/GuangchuangYu/ReactomePA/)
[![Last-changedate](https://img.shields.io/badge/last%20change-`r gsub('-', '--', Sys.Date())`-green.svg)](https://github.com/GuangchuangYu/ReactomePA/commits/master)
[![commit](http://www.bioconductor.org/shields/commits/bioc/ReactomePA.svg)](https://www.bioconductor.org/packages/devel/bioc/html/ReactomePA.html#svn_source)
[![GitHub forks](https://img.shields.io/github/forks/GuangchuangYu/ReactomePA.svg)](https://github.com/GuangchuangYu/ReactomePA/network) 
[![GitHub stars](https://img.shields.io/github/stars/GuangchuangYu/ReactomePA.svg)](https://github.com/GuangchuangYu/ReactomePA/stargazers) 


[![releaseVersion](https://img.shields.io/badge/release%20version-`r url="https://bioconductor.org/packages/release/bioc/html/ReactomePA.html"; x=readLines(url); gsub("\\D+(\\d+\\.\\d+\\.\\d+)\\D+", "\\1", x[grep("Version", x) +1])`-green.svg?style=flat)](https://bioconductor.org/packages/ReactomePA)
[![develVersion](https://img.shields.io/badge/devel%20version-`r x=readLines("DESCRIPTION"); y=x[grep("^Version", x)]; sub("Version: ", "", y)`-green.svg?style=flat)](https://github.com/GuangchuangYu/ReactomePA)
[![Bioc](http://www.bioconductor.org/shields/years-in-bioc/ReactomePA.svg)](https://www.bioconductor.org/packages/devel/bioc/html/ReactomePA.html#since)
[![post](http://www.bioconductor.org/shields/posts/ReactomePA.svg)](https://support.bioconductor.org/t/ReactomePA/)
[![download](http://www.bioconductor.org/shields/downloads/ReactomePA.svg)](https://bioconductor.org/packages/stats/bioc/ReactomePA/)


This package provides functions for pathway analysis based on REACTOME pathway database. It implements enrichment analysis, gene set enrichment analysis and several functions for visualization.

[![Twitter](https://img.shields.io/twitter/url/https/github.com/GuangchuangYu/ReactomePA.svg?style=social)](https://twitter.com/intent/tweet?hashtags=ReactomePA&url=https://guangchuangyu.github.io/ReactomePA)

------------------------------------------------------------------------

Please cite the following article when using `ReactomePA`: 

__*G Yu*__, QY He^\*^. ReactomePA: an R/Bioconductor package for reactome pathway analysis and visualization. __*Molecular BioSystems*__ 2016, 12(2):477-479.

[![doi](https://img.shields.io/badge/doi-1039/c5mb00663e-green.svg?style=flat)](http://dx.doi.org/1039/c5mb00663e)
[![citation](https://img.shields.io/badge/cited%20by-`r library(scholar); sum(get_article_cite_history('DO5oG40AAAAJ', '8d8msizDQcsC')$cites)`-green.svg?style=flat)](https://scholar.google.com.hk/scholar?oi=bibs&hl=en&cites=3311691878690959578)

------------------------------------------------------------------------

For details, please visit our project website, <https://guangchuangyu.github.io/ReactomePA>.

+ [Documentation](https://guangchuangyu.github.io/ReactomePA/documentation/)
+ [Featured Articles](https://guangchuangyu.github.io/ReactomePA/featuredArticles/)
+ [Feedback](https://guangchuangyu.github.io/ReactomePA/#feedback)

### Citation 

[![citation](https://img.shields.io/badge/cited%20by-`r library(scholar); sum(get_article_cite_history('DO5oG40AAAAJ', '8d8msizDQcsC')$cites)`-green.svg?style=flat)](https://scholar.google.com.hk/scholar?oi=bibs&hl=en&cites=3311691878690959578)


```{r echo=F, comment=NA}
d <- scholar::get_article_cite_history('DO5oG40AAAAJ', '8d8msizDQcsC')
txtplot::txtplot(d$year, d$cites)
```

### Download stats

[![download](http://www.bioconductor.org/shields/downloads/ReactomePA.svg)](https://bioconductor.org/packages/stats/bioc/ReactomePA/)
[![total](https://img.shields.io/badge/downloads-`r sum(dlstats::bioc_stats("ReactomePA")$Nb_of_downloads)`/total-blue.svg?style=flat)](https://bioconductor.org/packages/stats/bioc/ReactomePA/)
[![month](https://img.shields.io/badge/downloads-`r x <- dlstats::bioc_stats("ReactomePA"); x$Nb_of_downloads[nrow(x)-1]`/month-blue.svg?style=flat)](https://bioconductor.org/packages/stats/bioc/ReactomePA/)

```{r echo=F, comment=NA}
x <- dlstats::bioc_stats("ReactomePA")
x <- x[-nrow(x), ] # last month data is not complete
txtplot::txtplot(ggtree::Date2decimal(x$end), x$Nb_of_downloads, width=100, height=25)
```


