---
output:
  md_document:
    variant: gfm
html_preview: false
---


```{r echo=FALSE, results="hide", message=FALSE}
library("badger")
library("ypages")
```

# ReactomePA: Reactome Pathway Analysis

[![Project Status: Active - The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active)
`r badge_bioc_release("ReactomePA", "green")`
`r badge_devel("guangchuangyu/ReactomePA", "green")`
[![Bioc](http://www.bioconductor.org/shields/years-in-bioc/clusterProfiler.svg)](https://www.bioconductor.org/packages/devel/bioc/html/clusterProfiler.html#since)
[![platform](http://www.bioconductor.org/shields/availability/devel/ReactomePA.svg)](https://www.bioconductor.org/packages/devel/bioc/html/ReactomePA.html#archives)




```{r comment="", echo=FALSE, results='asis'}
cat(packageDescription('ReactomePA')$Description)
```


For details, please visit <https://yulab-smu.top/biomedical-knowledge-mining-book/>.


## :writing_hand: Authors

Guangchuang YU

School of Basic Medical Sciences, Southern Medical University

<https://yulab-smu.top>


------------------------------------------------------------------------

Please cite the following article when using `ReactomePA`:

__*G Yu*__, QY He^\*^. ReactomePA: an R/Bioconductor package for reactome pathway analysis and visualization. __*Molecular BioSystems*__ 2016, 12(2):477-479.


