---
output:
  md_document:
    variant: markdown_github
html_preview: false
---


```{r echo=FALSE, results="hide", message=FALSE}
library("ggtree")
library("txtplot")
library("ypages")
```

# ReactomePA: Reactome Pathway Analysis

`r badge_bioc_release("ReactomePA", "green")`
`r badge_devel("guangchuangyu/ReactomePA", "green")`
[![Bioc](http://www.bioconductor.org/shields/years-in-bioc/clusterProfiler.svg)](https://www.bioconductor.org/packages/devel/bioc/html/clusterProfiler.html#since)
`r badge_bioc_download("ReactomePA", "total", "blue")`
`r badge_bioc_download("ReactomePA", "month", "blue")`

[![Project Status: Active - The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active)
[![codecov](https://codecov.io/gh/GuangchuangYu/ReactomePA/branch/master/graph/badge.svg)](https://codecov.io/gh/GuangchuangYu/ReactomePA/)
[![Last-changedate](https://img.shields.io/badge/last%20change-`r gsub('-', '--', Sys.Date())`-green.svg)](https://github.com/GuangchuangYu/ReactomePA/commits/master)
[![commit](http://www.bioconductor.org/shields/commits/bioc/ReactomePA.svg)](https://www.bioconductor.org/packages/devel/bioc/html/ReactomePA.html#svn_source)
[![GitHub forks](https://img.shields.io/github/forks/GuangchuangYu/ReactomePA.svg)](https://github.com/GuangchuangYu/ReactomePA/network)
[![GitHub stars](https://img.shields.io/github/stars/GuangchuangYu/ReactomePA.svg)](https://github.com/GuangchuangYu/ReactomePA/stargazers)


[![platform](http://www.bioconductor.org/shields/availability/devel/ReactomePA.svg)](https://www.bioconductor.org/packages/devel/bioc/html/ReactomePA.html#archives)
[![Build Status](http://www.bioconductor.org/shields/build/devel/bioc/ReactomePA.svg)](https://bioconductor.org/checkResults/devel/bioc-LATEST/ReactomePA/)
[![Linux/Mac Travis Build Status](https://img.shields.io/travis/GuangchuangYu/ReactomePA/master.svg?label=Mac%20OSX%20%26%20Linux)](https://travis-ci.org/GuangchuangYu/ReactomePA)
[![AppVeyor Build Status](https://img.shields.io/appveyor/ci/Guangchuangyu/ReactomePA/master.svg?label=Windows)](https://ci.appveyor.com/project/GuangchuangYu/ReactomePA)



This package provides functions for pathway analysis based on REACTOME pathway database. It implements enrichment analysis, gene set enrichment analysis and several functions for visualization.

[![Twitter](https://img.shields.io/twitter/url/https/github.com/GuangchuangYu/ReactomePA.svg?style=social)](https://twitter.com/intent/tweet?hashtags=ReactomePA&url=http://pubs.rsc.org/en/Content/ArticleLanding/2016/MB/C5MB00663E#!divAbstract)

------------------------------------------------------------------------

Please cite the following article when using `ReactomePA`:

__*G Yu*__, QY He^\*^. ReactomePA: an R/Bioconductor package for reactome pathway analysis and visualization. __*Molecular BioSystems*__ 2016, 12(2):477-479.


`r badge_doi("10.1039/c5mb00663e", "green")`
`r badge_altmetric("4796667", "green")`
`r badge_citation("8d8msizDQcsC", "3311691878690959578", "green")`
`r badge_custom("ESI", "Highly Cited Paper", "green", "http://apps.webofknowledge.com/InboundService.do?mode=FullRecord&customersID=RID&IsProductCode=Yes&product=WOS&Init=Yes&Func=Frame&DestFail=http%3A%2F%2Fwww.webofknowledge.com&action=retrieve&SrcApp=RID&SrcAuth=RID&SID=Y2CXu6nry8nDQZcUy1w&UT=WOS%3A000368858900017")`


------------------------------------------------------------------------

For details, please visit our project website, <https://guangchuangyu.github.io/ReactomePA>.

+ [Documentation](https://guangchuangyu.github.io/ReactomePA/documentation/)
+ [Featured Articles](https://guangchuangyu.github.io/ReactomePA/featuredArticles/)
+ [Feedback](https://guangchuangyu.github.io/ReactomePA/#feedback)

### Citation

`r badge_citation("8d8msizDQcsC", "3311691878690959578", "green")`
`r badge_custom("ESI", "Highly Cited Paper", "green", "http://apps.webofknowledge.com/InboundService.do?mode=FullRecord&customersID=RID&IsProductCode=Yes&product=WOS&Init=Yes&Func=Frame&DestFail=http%3A%2F%2Fwww.webofknowledge.com&action=retrieve&SrcApp=RID&SrcAuth=RID&SID=Y2CXu6nry8nDQZcUy1w&UT=WOS%3A000368858900017")`


```{r echo=F, comment=NA}
d <- get_article_cite_history('DO5oG40AAAAJ', '8d8msizDQcsC')
txtplot(d$year, d$cites)
```

### Download stats

[![download](http://www.bioconductor.org/shields/downloads/ReactomePA.svg)](https://bioconductor.org/packages/stats/bioc/ReactomePA/)
`r badge_bioc_download("ReactomePA", "total", "blue")`
`r badge_bioc_download("ReactomePA", "month", "blue")`

```{r echo=F, comment=NA}
x <- dlstats::bioc_stats("ReactomePA")
x <- x[-nrow(x), ] # last month data is not complete
txtplot(Date2decimal(x$end), x$Nb_of_downloads, width=100, height=25)
```


