---
title: "An R package for Reactome Pathway Analysis"
author: "\\

	Guangchuang Yu (<guangchuangyu@gmail.com>)\\

        School of Public Health, The University of Hong Kong"
date: "`r Sys.Date()`"
bibliography: ReactomePA.bib
csl: nature.csl
output: 
  BiocStyle::html_document:
    toc: true
  BiocStyle::pdf_document:
    toc: true
vignette: >
  %\VignetteIndexEntry{An R package for Reactome Pathway Analysis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteDepends{org.Hs.eg.db}
  %\usepackage[utf8]{inputenc}
---

```{r style, echo=FALSE, results="asis", message=FALSE}
BiocStyle::markdown()
knitr::opts_chunk$set(tidy = FALSE,
                      warning = FALSE,
                      message = FALSE)
```

```{r echo=FALSE, results='hide', message=FALSE}
library(org.Hs.eg.db)
library(DOSE)
library(clusterProfiler)
library(ReactomePA)
```



# Introduction

This package is designed for reactome pathway-based analysis. Reactome
is an open-source, open access, manually curated and peer-reviewed
pathway database.

# Citation

If you use `r Biocpkg("Reactome")`[@yu_reactomepa_2016] in published research, please cite G. Yu (2015). In addition, please cite G. Yu (2012) when using `compareCluster` in `r Biocpkg("clusterProfiler")`, G Yu (2015) when applying enrichment analysis to NGS data using `r Biocpkg("ChIPseeker")`.

```
G Yu, QY He,
ReactomePA: an R/Bioconductor package for reactome pathway analysis and visualization.
Molecular BioSystems 2016, 12(2):477-479.
```

URL: [http://dx.doi.org/10.1039/C5MB00663E](http://dx.doi.org/10.1039/C5MB00663E)


```
G Yu, LG Wang, Y Han, QY He.
clusterProfiler: an R package for comparing biological themes among gene clusters.
OMICS: A Journal of Integrative Biology 2012, 16(5):284-287.
```

URL: [http://dx.doi.org/10.1089/omi.2011.0118](http://dx.doi.org/10.1089/omi.2011.0118)


```
G Yu, LG Wang, QY He.
ChIPseeker: an R/Bioconductor package for ChIP peak annotation, comparison and visualization.
Bioinformatics 2015, 31(14):2382-2383.
```

URL: [http://dx.doi.org/10.1093/bioinformatics/btv145](http://dx.doi.org/10.1093/bioinformatics/btv145)


# Supported organisms

Currently `r Biocpkg("ReactomePA")` supports several model organisms, including 'celegans', 'fly', 'human', 'mouse', 'rat', 'yeast' and 'zebrafish'. The input gene ID should be Entrez gene ID. We recommend using `clusterProfiler::bitr` to convert biological IDs. For more detail, please refer to [bitr: Biological Id TranslatoR](http://www.bioconductor.org/packages/release/bioc/vignettes/clusterProfiler/inst/doc/clusterProfiler.html#bitr-biological-id-translator).


# Pathway Enrichment Analysis

Enrichment analysis is a widely used approach to identify biological
themes. Here, we implement hypergeometric model to assess whether the
number of selected genes associated with reactome pathway is larger
than expected. The p values were calculated based the hypergeometric model[@boyle2004],

```{r}
library(ReactomePA)
data(geneList)
de <- names(geneList)[abs(geneList) > 1.5]
head(de)
x <- enrichPathway(gene=de,pvalueCutoff=0.05, readable=T)
head(summary(x))
```

For calculation/parameter details, please refer to the [vignette](http://www.bioconductor.org/packages/release/bioc/vignettes/DOSE/inst/doc/DOSE.html) of `r Biocpkg("DOSE")`.

## Pathway analysis of NGS data

Pathway analysis using NGS data (eg, RNA-Seq and ChIP-Seq) can be performed by linking coding and non-coding regions to coding genes via `r Biocpkg("ChIPseeker")` package, which can annotates genomic regions to their nearest genes, host genes, and flanking genes respectivly. In addtion, it provides a function, __*seq2gene*__, that simultaneously considering host genes, promoter region and flanking gene from intergenic region that may under control via cis-regulation. This function maps genomic regions to genes in a many-to-many manner and facilitate functional analysis. For more details, please refer to `r Biocpkg("ChIPseeker")`[@yu_chipseeker_2015].


## Visualize enrichment result
We implement barplot, dotplot enrichment map and category-gene-network for visualization. It is very common to visualize the enrichment result in bar or pie chart. We believe the pie chart is misleading and only provide bar chart.
```{r fig.height=5, fig.width=8}
barplot(x, showCategory=8)
```
```{r fig.height=8, fig.width=8}
dotplot(x, showCategory=15)
```

Enrichment map can be viusalized by __*enrichMap*__:
```{r fig.height=16, fig.width=20}
enrichMap(x, layout=igraph::layout.kamada.kawai, vertex.label.cex = 1)
```

In order to consider the potentially biological complexities in which a gene may belong to multiple annotation categories, we developed __*cnetplot*__ function to extract the complex association between genes and diseases.
```{r fig.height=12, fig.width=12}
cnetplot(x, categorySize="pvalue", foldChange=geneList)
```


## Comparing enriched reactome pathways among gene clusters with clusterProfiler
We have developed an `R` package `r Biocpkg("clusterProfiler")`[@yu_clusterprofiler:_2012] for comparing biological themes among gene clusters. `r Biocpkg("ReactomePA")` works fine with `r Biocpkg("clusterProfiler")` and can compare biological themes at reactome pathway perspective.

```{r fig.height=8, fig.width=13}
require(clusterProfiler)
data(gcSample)
res <- compareCluster(gcSample, fun="enrichPathway")
plot(res)
```

# Gene Set Enrichment Analysis
A common approach in analyzing gene expression profiles was identifying differential expressed genes that are deemed interesting. The __*enrichPathway*__ function we demonstrated previously were based on these differential expressed genes. This approach will find genes where the difference is large, but it will not detect a situation where the difference is small, but evidenced in coordinated way in a set of related genes. Gene Set Enrichment Analysis (GSEA)[@subramanian_gene_2005] directly addressed this limitation. All genes can be used in GSEA; GSEA aggregates the per gene statistics across genes within a gene set, therefore making it possible to detect situations where all genes in a predefined set change in a small but coordinated way. For algorithm details, please refer to the vignette of `r Biocpkg("DOSE")`[@yu_dose_2015].

```{r}
y <- gsePathway(geneList, nPerm=100, 
                minGSSize=120, pvalueCutoff=0.2, 
                pAdjustMethod="BH", verbose=FALSE)
res <- summary(y)
head(res)
```

## Visualize GSEA result
```{r fig.height=16, fig.width=16}
enrichMap(y)
```

```{r fig.height=8, fig.width=10}
gseaplot(y, geneSetID = "1280215")
```

# Pathway Visualization

In `r Biocpkg("ReactomePA")`, we also implemented __*viewPathway*__ to visualized the pathway.
```{r fig.height=16, fig.width=16}
viewPathway("E2F mediated regulation of DNA replication", readable=TRUE, foldChange=geneList)
```


# External documents

More documents can be found in <http://www.bioconductor.org/packages/DOSE>, <http://www.bioconductor.org/packages/clusterProfiler> and  <http://guangchuangyu.github.io/tags/reactomepa>.

## Bugs/Feature requests ##

If you have any, [let me know](https://github.com/GuangchuangYu/ReactomePA/issues).


# Session Information

Here is the output of `sessionInfo()` on the system on which this document was compiled:

```{r echo=FALSE}
sessionInfo()
```

# References
