---
title: "An R package for Reactome Pathway Analysis"
author: 
- name: Guangchuang Yu
  email: guangchuangyu@gmail.com
  affiliation: Department of Bioinformatics, School of Basic Medical Sciences, Southern Medical University
date: "`r Sys.Date()`"
biblio-style: apalike
output:
  prettydoc::html_pretty:
    toc: true
    theme: cayman
    highlight: github
  pdf_document:
    toc: true
vignette: >
  %\VignetteIndexEntry{An R package for Reactome Pathway Analysis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteDepends{org.Hs.eg.db}
  %\usepackage[utf8]{inputenc}
  %\VignetteEncoding{UTF-8}
---

```{r style, echo=FALSE, results="asis", message=FALSE}
knitr::opts_chunk$set(tidy = FALSE,
                      warning = FALSE,
                      message = FALSE)
```

```{r echo=FALSE, results='hide', message=FALSE}
CRANpkg <- function (pkg) {
    cran <- "https://CRAN.R-project.org/package"
    fmt <- "[%s](%s=%s)"
    sprintf(fmt, pkg, cran, pkg)
}

Biocpkg <- function (pkg) {
    sprintf("[%s](http://bioconductor.org/packages/%s)", pkg, pkg)
}

library(org.Hs.eg.db)
library(DOSE)
library(ReactomePA)
```




# Vignette

Please go to <https://yulab-smu.top/biomedical-knowledge-mining-book/> for the full vignette.


# Citation

If you use `r Biocpkg("ReactomePA")` [@yu_reactomepa_2016] in published research, please cite:

__*G Yu*__, QY He^\*^. ReactomePA: an R/Bioconductor package for reactome pathway analysis and visualization. __*Molecular BioSystems*__ 2016, 12(2):477-479. doi: [10.1039/C5MB00663E](http://dx.doi.org/10.1039/C5MB00663E)



# Need help?


If you have questions/issues, please post to [Bioconductor support site](https://support.bioconductor.org/) and tag your post with *ReactomePA*.

